Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-18 journal paper/content/sec-intro.tex
Added a para on time-discounting.

Learning from interactions with users is ubiquitous in modern customer-facing platforms, from product recommendations to web search to content selection to fine-tuning user interfaces. Many platforms purposefully implement \emph{exploration}: making potentially suboptimal choices for the sake of acquiring new information.
Online platforms routinely deploy A/B tests, and are increasingly adopting  more sophisticated exploration methodologies based on \emph{multi-armed bandits}, a well-known framework for exploration and making decisions under uncertainty.

@@

\xhdr{Assumptions.}
Our models are stylized in several important  respects, some of which we discuss below. Firms compete only on the quality of service, rather than, say, pricing or the range of products. Agents are myopic: they do not worry about how their actions impact their future utility.\footnote{In particular, agents do not attempt to learn over time, to second-guess or game future agents, or to manipulate the principals' learning algorithms. This is arguably typical in practice, in part because one agent's influence tends to be relatively small.}  Various performance signals available to the users, from personal experience to word-of-mouth to consumer reports, are abstracted as persistent ``reputation scores", and further simplified to average performance over a time window. On the machine learning side, our setup is geared to distinguish between ``simple" vs. ``better" vs. ``smart" bandit algorithms; we are not interested in state-of-art algorithms for very realistic bandit settings.

@@

>>>>

Learning from interactions with users is ubiquitous in modern customer-facing platforms, from product recommendations to web search to content selection to fine-tuning user interfaces. Many platforms purposefully implement \emph{exploration}: making potentially suboptimal choices for the sake of acquiring new information.
Online platforms routinely deploy A/B tests, and are increasingly adopting  more sophisticated exploration methodologies based on \emph{multi-armed bandits}, a standard and well-studied framework for exploration and making decisions under uncertainty
\citep{Gittins-book11,Bubeck-survey12,slivkins-MABbook,LS19bandit-book}.

@@

\xhdr{Modeling.}
Our models are stylized in several important  respects. Firms compete only on the quality of service, rather than, say, pricing or the range of products. Agents are myopic: they do not worry about how their actions impact their future utility.\footnote{In particular, agents do not attempt to learn over time, to second-guess or game future agents, or to manipulate the principals' learning algorithms. This is arguably typical in practice, in part because one agent's influence tends to be relatively small.}  Various performance signals available to the users, from personal experience to word-of-mouth to consumer reports, are abstracted as persistent ``reputation scores", and further simplified to average performance over a time window. On the machine learning side, our setup is geared to distinguish between ``simple" vs. ``better" vs. ``smart" bandit algorithms; we are not interested in state-of-art algorithms for very realistic bandit settings.

@@

\asedit{Principals' utilities (and, accordingly, bandit rewards) are not discounted with time. While much of the early work focuses on  time-discounted bandits \citep{Gittins-book11}, non-discounted  formulations are prevalent in the bandits literature over the past two decades \citep{slivkins-MABbook,LS19bandit-book}, and better correspond to practical deployments \citep[\eg][]{DS-arxiv}. Moreover, the distinctions between better and worse bandit algorithms are not as well-understood under time-discounting.}
